ADJACENT STATES ARIMAX MODEL - with log-back transformations

### 2025-06-23 models_with_logback/ES_ADJACENT/ADJACENT.Rmd
update
comments reviewed

Here we run ensembles and single automatic ARIMAX models for forecasting weekly hospitalizations in states on the contiguous U.S. These model use mean hospitalizations in adjacent states as exogenous variables. The models fit on a rolling window of previous 104 weeks for the state under analysis and a rolling windows with the same size with 1 week-lag for the exogenous variables to generate forecasts. These models include log-back transformations. It return some metrics that evaluate the performance of the models:target_end_date, abs_error, cases, forecast, 'N_of_models", weighted interval score (WIS), predictive quantiles. The user can choose a  single best automatic ARIMAXs (auto=TRUE), or ensembles of 27 permutations of 0,1,2 pdq's (ES27=TRUE) or 64 permutations of 0,1,2,3 pdq's (ES64=TRUE). The user also chooses the number of weeks ahead for each forecast, and the size of the rolling window which is set as 2 years (104 weeks).

@@

IF YOU WANT A FAST RESULT RUN ONLY THE AUTO_example, the others take longer.

>>>>

Here we run ensembles and single automatic ARIMAX models for forecasting weekly hospitalizations in 48 states on the contiguous U.S. These model use mean hospitalizations in adjacent states as exogenous variables. The models fit on a rolling window of previous 104 weeks for the state under analysis and a rolling windows with the same size with 1 week-lag for the exogenous variables to generate forecasts. These models include log-back transformations. It return some metrics that evaluate the performance of the models:target_end_date, abs_error, cases, forecast, 'N_of_models", weighted interval score (WIS), predictive quantiles. The user can choose a  single best automatic ARIMAXs (auto=TRUE), or ensembles of 27 permutations of 0,1,2 pdq's (ES27=TRUE) or 64 permutations of 0,1,2,3 pdq's (ES64=TRUE). The user also chooses the number of weeks ahead for each forecast, and the size of the rolling window which is set as 2 years (104 weeks).

@@
